---
title: "Lab 00 - Hello IDS!"
author: "junsongtang"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Tang Junsong", "Lu Junxi", "Lu Yiming", 
           "Deng Jieming", "Guo Zeyu", "Zhang Boning"),
  github_username = c("junsongtang", "LU", "YimingLuKevin", 
                      "Branddenj", "Zeyu Guo", "Jona"), 
  colour = c("white", "red", "Black", 
             "green", "purple", "white"),
  hobby = c("playing guitar", "fitness", "weight training", 
            "photography", "basketball", "gym"),
  favourite_number = c(7, 5, 1, 3, 5, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


This plot shows the Branddenj's favourite colour is green, favourite number is 3, the Jona's favourite colour is white, favourite number is 3, the junsongtang's favourite colour is white, favourite number is 7, the LU's favourite colour is red, favourite number is 5, the YimingLuKevin's favourite colour is black, favourite number is 1, the Zeyu Guo's favourite colour is purple, favourite number is 5.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github_username", 
          y = "favourite_number",
          title = "favourite")
```



### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Use different colour to represent different hobbies, take the names of team members as x-axis, put the squares of colour to different members to show their hobbies.
